---
title: "Source Data"
output:
  html_document:
    df_print: paged
---


```{r include=FALSE}

library(tidyverse)
library(zoo)
library(sf)
library(tmap)
library(jsonlite)
library(lubridate)

```


# Lab-Confirmed Cases

```{r include=FALSE}
json_cases <- fromJSON("https://coronavirus.data.gov.uk/downloads/json/coronavirus-cases_latest.json", flatten = TRUE)

last_acquired <- Sys.time()
last_updated <- ymd_hms(json_cases$metadata$lastUpdatedAt)
```

Lab confirmed cases data is acquired from the JSON feed available from the [UK Government Coronavirus Dashboard](https://coronavirus.data.gov.uk/). This data was last acquired at **`r last_acquired`**. The data was last updated at **`r last_updated`**.

## All Lower Tier Local Authority Cases

The data contains numbers of lab-confirmed cases by each lower-tier local authority for each day. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ltla_cases <- json_cases$ltlas %>% 
  mutate(specimenDate = ymd(specimenDate))

ltla_cases %>% 
  group_by(specimenDate) %>% 
  summarise(total_cases = sum(dailyLabConfirmedCases)) %>% 
  ggplot(aes(specimenDate, total_cases)) + 
  geom_bar(stat = "identity") + 
  ggtitle("Total Cases for All Lower Tier Local Authorities")

saveRDS(ltla_cases, "./source-data/ltla-cases.RDS")
```

Note that confirmed cases for the last few days are likely to be further updated over the coming days.

## Disclaimer

The cases data has the following disclaimer.

```{r echo=FALSE}
json_cases$metadata$disclaimer
```

# Lower Tier Local Authority Maps

Map geometry is sourced from [ONS Geography Open Data](https://hub.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0).

```{r echo=FALSE, message=FALSE, warning=FALSE}
map <- st_read("https://opendata.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0.geojson")

saveRDS(map, "./source-data/map.RDS")

tmap_mode("view")

qtm(map)

```

